---
title: "Computing Expected Violence Exposure"
author: "Jonathan Che"
date: "10 April 2017"
output: 
  pdf_document:
    fig_height: 3
    fig_width: 5
  html_document:
    fig_height: 3
    fig_width: 5
  word_document:
    fig_height: 3
    fig_width: 5
---


```{r, include=FALSE}
require(mosaic)
require(dplyr)
require(readr)
require(stringr)
```

```{r, include=FALSE}
# Some customization.  You can alter or delete as desired (if you know what you are doing).

# This changes the default colors in lattice plots.
trellis.par.set(theme=theme.mosaic())  

# knitr settings to control how R chunks work.
require(knitr)
opts_chunk$set(
  tidy=FALSE,     # display code as typed
  size="small"    # slightly smaller font for code
)
```

## Overview

In Dahl and DellaVigna's paper "Does Movie Violence Increase Violent Crime?", they find that the "incapacitation effect" outweighs the "arousal effect" (details in paper summary). In their analyses, they use kids-in-mind.com's violence ratings to measure public exposure to movie violence.

To get a better understanding of the differen effects of incapacitation and arousal, I build a model to predict "expected" exposure to violence, as opposed to kids-in-mind.com's "actual" exposure to violence scores. The variation between "expected" and "actual" violence will drive my regression analyses.

In this document, I will first perform a proxy replication of how Dahl and DellaVigna calculate public exposure to movie violence to see how my methods compare to theirs. I do this for a few reasons. First, I cannot directly view the methods that Dahl and DellaVigna use to calculate public exposure to movie violence. Though I have the final computed values, I don't have the specifics of how they were calculated. Thus, before I calculate my "expected exposure" scores, I want to check that my methods are at least similar to theirs. Second, I will not (at least for now) be imputing any box office sales like Dahl and DellaVigna do (Appendix I). Thus, my results will definitely be different from theirs. I want to check that the magnitude of this difference is not too extreme before proceeding. To check for similarity, I will just examine a scatterplot (and the R^2).

Then, I will use a regression methodology to compute "expected exposure" scores. I will base these predictions on the movie's MPAA rating, and its genre.

## Method

First, I pull in all the data that I will need.

```{r}
movie_ratings <- readRDS("movie_ratings.rds")
movie_sales <- readRDS("movie_sales.rds")
ticket_prices <- read_csv("ticket_prices.csv")
```

"We deflate... the daily box-office sales by the average price of a ticket" (Dahl and DellaVigna 690)

```{r}
movie_sales <- movie_sales %>%
  left_join(ticket_prices, by="Year") %>%
  mutate(tickets = Gross/Price)
```

"We match the box-office data to violence ratings from kids-in-mind.com... we group movies into three categories: strongly violent, mildly violent, and nonviolent" (690). 0-4 is nonviolent, 5-7 is mildly violent, 8-10 is violent.

```{r}
# Some data cleaning first
movie_ratings <- movie_ratings %>%
  select(Title, Year, MPAA_Rating, Violence) %>%
  mutate(Year = as.numeric(as.character(Year))) %>%
  mutate(Violence = as.numeric(as.character(Violence))) %>%
  mutate(MPAA_Rating = as.character(MPAA_Rating)) %>%
  mutate(MPAA_Rating = str_replace_all(MPAA_Rating, "[-\\[\\]]", ""))

movie_ratings <- movie_ratings %>%
  mutate(viol_strong = Violence >= 8) %>%
  mutate(viol_mild = (Violence >=5 & Violence <= 7)) %>%
  mutate(viol_non = Violence <= 4)
```

Now, we merge the two data frames by movie title.

```{r, warning=FALSE}
# Kids in mind parses "The ___" movies as "___, The" (same as "A ___")
movie_ratings <- movie_ratings %>%
  mutate(Title = ifelse(str_detect(Title, ", The"), 
                        str_c("The ", str_replace(Title, ", The", "")), 
                        as.character(Title))) %>%
  mutate(Title = ifelse(str_detect(Title, ", A"), 
                        str_c("A ", str_replace(Title, ", A", "")), 
                        as.character(Title)))
# Manual method of matching some more difficult names
movie_ratings <- movie_ratings %>%
  mutate(Title = ifelse(Title == "Dr. Dolittle", "Doctor Dolittle",
                 ifelse(Title == "Star Wars: Episode II - Attack of the Clones", "Star Wars Ep. II: Attack of the Clones",
                 ifelse(Title == "Star Wars Episode I: The Phantom Menace", "Star Wars Ep. I: The Phantom Menace",
                 ifelse(Title == "The Lord of the Rings: Return of the King", "The Lord of the Rings: The Return of the King",
                 ifelse(Title == "Jurassic Park III", "Jurassic Park 3",
                 ifelse(Title == "Men In Black II", "Men in Black 2",
                 ifelse(Title == "X2: X-Men United", "X2", Title))))))))
# Box office info parsed this title stranglely
movie_sales <- movie_sales %>%
  mutate(Title = ifelse(str_detect(Title, "Harry Potter and the Sorcerer"),
                        "Harry Potter and the Sorcerer's Stone",
                        as.character(Title)))

# Unusual coding to deal with movies with same title in different years, or same movie spanning different years
# Assume that two movies with the same title don't come out in consecutive years
movie_ratings2 <- movie_ratings %>%
  mutate(Year = Year+1)
movie <- movie_sales %>%
  left_join(movie_ratings, by=c("Title", "Year")) %>%
  left_join(movie_ratings2, by=c("Title", "Year")) %>%
  mutate(MPAA_Rating = ifelse(is.na(MPAA_Rating.x), MPAA_Rating.y, MPAA_Rating.x)) %>%
  mutate(Violence = ifelse(is.na(Violence.x), Violence.y, Violence.x)) %>%
  mutate(viol_strong = ifelse(is.na(viol_strong.x), viol_strong.y, viol_strong.x)) %>%
  mutate(viol_mild = ifelse(is.na(viol_mild.x), viol_mild.y, viol_mild.x)) %>%
  mutate(viol_non = ifelse(is.na(viol_non.x), viol_non.y, viol_non.x)) %>%
  select(-MPAA_Rating.x, -Violence.x, -viol_strong.x, -viol_mild.x, -viol_non.x,
         -MPAA_Rating.y, -Violence.y, -viol_strong.y, -viol_mild.y, -viol_non.y)
movie$MPAA_Rating = as.factor(movie$MPAA_Rating)
```

Finally, we can compute the daily exposure to movie violence.

```{r}

```


