---
title: "Web Scraping Movie Data"
author: "Jonathan Che"
date: "8 April 2017"
output: 
  pdf_document:
    fig_height: 3
    fig_width: 5
  html_document:
    fig_height: 3
    fig_width: 5
  word_document:
    fig_height: 3
    fig_width: 5
---


```{r, include=FALSE}
require(mosaic)
require(rvest)
require(readr)
require(stringr)
```

```{r, include=FALSE}
# Some customization.  You can alter or delete as desired (if you know what you are doing).

# This changes the default colors in lattice plots.
trellis.par.set(theme=theme.mosaic())  

# knitr settings to control how R chunks work.
require(knitr)
opts_chunk$set(
  tidy=FALSE,     # display code as typed
  size="small"    # slightly smaller font for code
)
```

## Overview

The kids-in-mind website has an alphabetical listing of all of their rated movies, but I cannot view all of them on one page. My goal here is to simply get all of the movies into one dataset.

## Method

First, I make an empty matrix that's large enough to hold all 4503 movies on kids-in-mind.com.

```{r, error=FALSE}
mat_master <- matrix(NA, nrow=4507, ncol=6)   # 4503 films on kids-in-mind.com
```

Then, I construct a function that can iteratively scrape the information from each page.

```{r}
add_movies <- function(x){
  url <- str_c(url1, x, url2, sep="")
  webpage <- read_html(url)
  string <- webpage %>%
    html_nodes(".t11normal+ p") %>%
    html_text()
  split_string <- str_split(string, "\n\n")[[1]]
  split_string <- split_string[2:(length(split_string)-1)]
  
  KIM_rating <- word(split_string, -1) %>%
    str_split("[.]")
  MPAA_rating <- word(split_string, -3) %>%
    str_sub(2,-2)
  Year <- word(split_string, -4) %>%
    str_sub(2,-2)
  Title <- word(split_string, 1, -5)
  
  temp <- cbind(Title, Year, MPAA_rating, do.call(rbind, KIM_rating))
  for (n in 1:dim(temp)[1]){
    mat_master[(n+x),] <<- temp[n,]   # Assign value to global variable
  }
}
```

Now, I loop through all the relevant pages of kids-in-mind.com

```{r, warning=FALSE, error=FALSE}
vec <- seq(from=0, to=4488, by=34)   # 4488 is label of last page
url1 <- "http://www.kids-in-mind.com/cgi-bin/listbyrating/search.pl?query=&stpos="
url2 <- "&stype=AND&s1=0&s2=10&v1=0&v2=10&p1=0&p2=10&m=1&m=2&m=3&m=4"

for(i in vec){
  add_movies(i)
}
```

Finaly, I output the master data frame

```{r}
movie_ratings <- data.frame(mat_master)
names(movie_ratings) <- c("Title", "Year", "MPAA_Rating", "Sex", "Violence", "Profanity")
write_csv(movie_ratings, path="movie_ratings.csv")
saveRDS(movie_ratings, "movie_ratings.rds")
```

