---
title: "Web Scraping Movie Genre Data"
author: "Jonathan Che"
date: "11 April 2017"
output: 
  pdf_document:
    fig_height: 3
    fig_width: 5
  html_document:
    fig_height: 3
    fig_width: 5
  word_document:
    fig_height: 3
    fig_width: 5
---

```{r, include=FALSE}
require(mosaic)
require(rvest)
require(readr)
require(stringr)
require(data.table)
```

```{r, include=FALSE}
# Some customization.  You can alter or delete as desired (if you know what you are doing).

# This changes the default colors in lattice plots.
trellis.par.set(theme=theme.mosaic())  

# knitr settings to control how R chunks work.
require(knitr)
opts_chunk$set(
  tidy=FALSE,     # display code as typed
  size="small"    # slightly smaller font for code
)
```

## Overview

I use information from the-numbers.com to extract, for the top 10 movies of each year, their genre and a text description of their rating.

## Method

First, I do some variable setup.

```{r}
url1 <- "http://www.the-numbers.com/market/"
url2 <- "/summary"
years <- seq(from=1998, to=2004)
master_list <- list()   # For the years
movie_info_list <- list()   # For the 10 movies in a year
#movie_info_df <- data.frame()
```

Next, I make a function that does the following:
1) Go to the "summary" page for a given year
2) Visit each of the top 10 movies for that year
3) Pull genre/MPAA Rating Description information for each of those movies

```{r}
year <- 2000

extract_year <- function(year){
  url <- str_c(url1, year, url2, sep="")
  webpage <- read_html(url)
  movie_names <- webpage %>%
    html_nodes("table:nth-child(1) b a") %>%
    html_text()
  movie_urls <- webpage %>%
    html_nodes("table:nth-child(1) b a") %>%
    html_attr("href")
  movie_urls <- str_c("http://www.the-numbers.com", movie_urls)
  
  for(i in 1:10){
    moviepage <- movie_urls[i]
    info_table <- moviepage %>%
      read_html() %>%
      # html_nodes(xpath=`//*[(@id = "box_office_chart") and (((count(preceding-sibling::*) + 1) = 8) and parent::*)]`) %>%
      # html_nodes(xpath=`//*[@id="box_office_chart"]/table`) %>%
      # html_nodes("#box_office_chart:nth-child(8)") %>%
      html_nodes("h2+ table") %>%
      html_table()
    info_table <- info_table[[1]]
    info_table <- info_table %>%
      filter(str_detect(X1, "MPAA")|str_detect(X1, "Genre"))
    movie_info_list[[i]] <<- data.table(Title=movie_names[i], Genre=info_table$X2[2], Info=info_table$X2[1])
    #movie_info_list[[i]] <<- list(movie_names[i], info_table$X2[2], info_table$X2[1])
    #movie_info_df <<- rbind(movie_info_df, c(movie_names[i], info_table$X2[2], info_table$X2[1]))
  }
  count <- year - years[1] + 1
  master_list[[count]] <<- rbindlist(movie_info_list, use.names=TRUE)
  #master_list[[count]] <<- movie_info_df
}
```

Then, I run the function on years 1998-2004.

```{r}
for (i in years){
  extract_year(i)
  # print(str_c("Finished ", i, sep=""))
}
movie_genres <- rbindlist(master_list)
```

At this point, the data are consolidated. I export a csv and a rda file.

```{r}
write_csv(movie_genres, path="movie_genres.csv")
saveRDS(movie_genres, "movie_genres.rds")
```

